\documentclass[12pt]{article}

% Packages
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{scrextend}
\usepackage{titlesec}

\usepackage[margin=1in]{geometry}

\usepackage[style=numeric,maxbibnames=99,sorting=none]{biblatex}
\addbibresource{tex/publications.bib}
\DeclareNameAlias{default}{given-family}

% Change how each biblatex bib heading is printed
\defbibheading{bibliography}[\refname]{%
  \subsubsection*{\normalfont\textit{#1}}%
}

% No translations, only English
\newcommand{\email}{joel.oskarsson@outlook.com}

% Title format
\titleformat{\section}
  {\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\normalsize\itshape}{\thesubsection}{1em}{}



\newcommand{\inputsection}[1]{\input{tex/sections/#1}}

\graphicspath{{./graphics/}}

\pagenumbering{gobble}
\usepackage[utf8]{inputenc}

\begin{document}

\inputsection{header}
\inputsection{research_interests}
\inputsection{education}
\inputsection{employment}
\inputsection{presentations}
\inputsection{reviewing}
\inputsection{event_participation}

\section*{Other activities}
\begin{itemize}
    \item Regularly act as reviewer for established machine learning conferences and associated workshops. Including:
        AISTATS,
        ICLR,
        NeurIPS.
    \item Organizer of the \href{https://github.com/STIMALiU/ml-reading-group}{STIMA Machine Learning Reading Group} at Linköping University (2022--)
    \item Research visits, long and short (UCL, ECMWF, ETH/Meteoswiss, WASP finland trip?)
    \item Regular attendance at international conferences and workshops within machine learning.
    \item Media coverage https://www.svt.se/nyheter/lokalt/ost/de-vill-gora-vaderprognoser-mer-palitliga-med-hjalp-av-ai
    \item Creator and maintainer of the \href{https://github.com/mllam/neural-lam}{Neural-LAM} open source python library for machine learning weather forecsating models.
    \item ML-LAM online meetups
\end{itemize}

\section*{Specific Skills and Knowledge}
\begin{itemize}
    \item Extensive knowledge of models and algorithms for modern \textbf{machine learning and AI} applications. Specific expertise in:
    \begin{itemize}
        \item Graph neural networks
        \item Bayesian models and inference methods
        \item Probabilistic deep learning
    \end{itemize}

\item Sound knowledge of good \textbf{software engineering} practices, acquired from courses and projects throughout my undergraduate studies.
        % I apply these practices to my research projects, creating accessible code.
        % To emphasize transparency and reproducability in research I have made a habit to release research code publicly (see \href{my github page}{https://github.com/joeloskarsson}).

    \item Programming languages and frameworks
    \begin{description}
        \item [Knowledgeable in] Python, PyTorch, PyTorch Geometric and SciPy/NumPy.
        \item [Experience with] R, Tensorflow, scikit-learn, Java, MATLAB and C++.
    \end{description}

\item Highly accustomed to working in \textbf{Linux} environments.
\end{itemize}

\end{document}
